--- 
title: "Code folding!"
author: Alicia A. Johnson
documentclass: book
output: 
  bookdown::gitbook:
    includes:
      in_header: header.html
      after_body: footer.html
---


```{r htmlTemp3, echo=FALSE, eval=TRUE}
# Keep this chunk to use code folding
codejs       <- readr::read_lines("js/codefolding.js")
collapsejs   <- readr::read_lines("js/collapse.js")
transitionjs <- readr::read_lines("js/transition.js")

# Create header.html
htmlhead <- 
  paste('
<script>',
paste(transitionjs, collapse = "\n"),
'</script>
<script>',
paste(collapsejs, collapse = "\n"),
'</script>
<script>',
paste(codejs, collapse = "\n"),
'</script>
<style type="text/css">
.code-folding-btn { margin-bottom: 4px; }
.row { display: flex; }
.collapse { display: none; }
.in { display:block }
</style>
<script>
$(document).ready(function () {
  window.initializeCodeFolding("show" === "show");
});
</script>
', sep = "\n")

readr::write_lines(htmlhead, path = "header.html")
```



\
\



# Try it out

**Attribution**


The materials in this repository provide the structure needed to incorporate code folding in an Rbookdown.  Proper attribution:

- footer.html from [shilad](https://github.com/shilad)    
- overall workflow inspired by this [stackoverflow post](https://stackoverflow.com/questions/45360998/code-folding-in-bookdown/45501553)    

- collapse.js & transition.js files: Copyright 2011-2016 Twitter, Inc. Licensed under MIT (https://github.com/twbs/bootstrap/blob/master/LICENSE)



\
\
\
\




**Final product**

You can check out the final result [here](https://ajohns24.github.io/bookdown_codefolding/).


\
\
\
\





**Let's try it!**


\


**Question:**  Have you been hearing all of the news about corduroy pillows?    

\

**Answer:**    

<div class = "solution">  
They're making *head lines*!
</div>



\
\
\
\



**Question:**  How was this plot made?    

```{r echo = FALSE}
sim_data <- data.frame(x = rnorm(100))
sim_data$y <- rnorm(100, mean = sim_data$x + 1)
plot(y ~ x, sim_data)
```


\




**Answer:**    

<div class = "solution">  
```{r eval = FALSE}
sim_data <- data.frame(x = rnorm(100))
sim_data$y <- rnorm(100, mean = sim_data$x + 1)
plot(y ~ x, sim_data)
```
</div>





 
\
\
\
\




\
\
\
\
\
\





